This page contains tables showing which channels are accessed by which channel commands on different versions of the Poly\-D\-A\-Q 2 board. These channel commands can be used in the data logger configuration file and when communicating with a Poly\-D\-A\-Q through the dumb terminal.

All commands are {\bfseries case} {\bfseries sensitive}. For example, typing {\bfseries D} will cause the Poly\-D\-A\-Q to perform an A/\-D conversion on the channel specified by the hexadecimal number D (decimal 13), but typing {\bfseries d} will cause the Poly\-D\-A\-Q to show the results of a memory dump (a programming diagnostic tool).

When a command is not understood by the Poly\-D\-A\-Q, it shows the command which has confused it and asks, \char`\"{}\-What's That Function?\char`\"{}\hypertarget{pd_channels_pd_044}{}\section{Poly\-D\-A\-Q 0-\/4-\/4}\label{pd_channels_pd_044}
This version of the Poly\-D\-A\-Q 2 board is designed for use in the M\-E 410 course, which makes heavy use of strain gauges. It has four strain gauge bridge amplifiers and four voltage inputs. Two of the voltage inputs accept -\/10 to +10\-V inputs and the other two accept 0 to 3.\-3\-V inputs with finer resolution. If present, an onboard M\-M\-A8452\-Q accelerometer provides 3 axes of acceleration data. An external M\-M\-A8452\-Q accelerometer can be connected to the board's I2\-C bus; if present, the external accelerometer is accessed as shown in the table.

The given calibration numbers (slope and offset) are approximate and for convenience only. The user should check all calibrations carefully using a high-\/accuracy voltmeter. In many cases, entering a slope of 1.\-0 and offset of 0.\-0 to cause raw A/\-D output numbers to be recorded is the best option.

\begin{TabularC}{5}
\hline
\rowcolor{lightgray}\PBS\centering {\bf Channel }&\PBS\centering {\bf Command }&\PBS\centering {\bf Slope }&\PBS\centering {\bf Offset }&{\bf Description  }\\\cline{1-5}
\PBS\centering {\ttfamily S1} &\PBS\centering {\ttfamily E} &\PBS\centering 0.\-00806 (1) &\PBS\centering (2) &Strain gauge bridge 1 \\\cline{1-5}
\PBS\centering {\ttfamily S2} &\PBS\centering {\ttfamily F} &\PBS\centering 0.\-00806 (1) &\PBS\centering (2) &Strain gauge bridge 2 \\\cline{1-5}
\PBS\centering {\ttfamily S3} &\PBS\centering {\ttfamily 9} &\PBS\centering 0.\-00806 (1) &\PBS\centering (2) &Strain gauge bridge 3 \\\cline{1-5}
\PBS\centering {\ttfamily S4} &\PBS\centering {\ttfamily 8} &\PBS\centering 0.\-00806 (1) &\PBS\centering (2) &Strain gauge bridge 4 \\\cline{1-5}
\PBS\centering &\PBS\centering &\PBS\centering &\PBS\centering &\\\cline{1-5}
\PBS\centering {\ttfamily V1} &\PBS\centering {\ttfamily A} &\PBS\centering 0.\-00513 &\PBS\centering -\/8.\-8537 &Voltage channel 1 (-\/10 to +10\-V) \\\cline{1-5}
\PBS\centering {\ttfamily V2} &\PBS\centering {\ttfamily B} &\PBS\centering 0.\-00513 &\PBS\centering -\/8.\-8537 &Voltage channel 2 (-\/10 to +10\-V) \\\cline{1-5}
\PBS\centering {\ttfamily V3} &\PBS\centering {\ttfamily C} &\PBS\centering 0.\-000806 &\PBS\centering 0.\-0 &Voltage channel 3 (0 to +3.3\-V) \\\cline{1-5}
\PBS\centering {\ttfamily V4} &\PBS\centering {\ttfamily D} &\PBS\centering 0.\-000806 &\PBS\centering 0.\-0 &Voltage channel 4 (0 to +3.3\-V) \\\cline{1-5}
\PBS\centering &\PBS\centering &\PBS\centering &\PBS\centering &\\\cline{1-5}
\PBS\centering {\ttfamily X} &\PBS\centering {\ttfamily X} &\PBS\centering 0.\-000061 (3) &\PBS\centering 0.\-0 &Onboard accelerometer X axis \\\cline{1-5}
\PBS\centering {\ttfamily Y} &\PBS\centering {\ttfamily Y} &\PBS\centering 0.\-000061 (3) &\PBS\centering 0.\-0 &Onboard accelerometer Y axis \\\cline{1-5}
\PBS\centering {\ttfamily Z} &\PBS\centering {\ttfamily Z} &\PBS\centering 0.\-000061 (3) &\PBS\centering 0.\-0 &Onboard accelerometer Z axis \\\cline{1-5}
\PBS\centering &\PBS\centering &\PBS\centering &\PBS\centering &\\\cline{1-5}
\PBS\centering {\ttfamily x} &\PBS\centering {\ttfamily x} &\PBS\centering 0.\-000061 (3) &\PBS\centering 0.\-0 &External accelerometer X axis \\\cline{1-5}
\PBS\centering {\ttfamily y} &\PBS\centering {\ttfamily y} &\PBS\centering 0.\-000061 (3) &\PBS\centering 0.\-0 &External accelerometer Y axis \\\cline{1-5}
\PBS\centering {\ttfamily z} &\PBS\centering {\ttfamily z} &\PBS\centering 0.\-000061 (3) &\PBS\centering 0.\-0 &External accelerometer Z axis \\\cline{1-5}
\end{TabularC}
Notes\-: \par
 (1) The given slope converts A/\-D output to bridge differential voltage in m\-V. \par
 (2) Bridge amplifier offset varies depending on bridge balance. \par
 (3) When the accelerometer is configured for +/-\/2g range, as is its default. 